Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 paper.qmd
axes of fig 10 - PH

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs_deselected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, colour = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, colour = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("b1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))

@@

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs_deselected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, colour = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, colour = "#800026", size = 3) +
  xlab(expression(e[hj])) +
  ylab("") +
  interior_annotation("a1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15))
```

>>>>

error_plot_one_curvy_hist_selected <- ggplot(error_df_one_curvy_abs_deselected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, colour = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected11, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, colour = "#800026", size = 3) +
  xlab(expression(paste("residual (",e[hi],")"))) +
  ylab("") +
  interior_annotation("b1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_blank())

@@

error_plot_one_curvy_hist <- ggplot(error_df_one_curvy_abs_deselected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density)) +
  geom_point(alpha=0.7, colour = "#d9d9d9") +
  geom_point(data = error_df_one_curvy_abs_selected12, 
      aes(x = sqrt_row_wise_total_error, 
          y = density),
      alpha=0.7, colour = "#800026", size = 3) +
  xlab(expression(paste("residual (",e[hi],")"))) +
  ylab("") +
  interior_annotation("a1",
                      cex = 2) +
  theme_bw() +
  theme(aspect.ratio = 1,
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 15),
        axis.text.y = element_blank())
```
